%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PlushCV - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (11/28/2021)
%
% Author:
% Shubham Mazumder (http://mazumder.me)
%
% Hacked together from:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Figure out a smoother way for the document to flow onto the next page.
% 3. Add more icon options 
% 4. Fix hacky left alignment on contact line
% 5. Remove Hacky fix for awkward extra vertical space
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the vertical limit.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Icons:
%%Main: https://icons8.com/icons/carbon-copy
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{plushcv}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{\fontsize{35}{45}\selectfont Rushikesh}{\fontsize{35}{45}\selectfont Waghmode}{AI/ML Engineer}{\fontsize{10}{20}\selectfont\contactline{\href{https://www.github.com/BeastRWA8938}{BeastRWA8938}}{\href{https://www.linkedin.com/in/rushikesh-waghmode-967162239/}{li-Rushikesh}}{\href{mailto:rushikeshwaghmode688@gmail.com}{rushikeshwaghmode688@gmail.com}}{\href{tel:+917620451904}{7620451904}}}

% \namesection{Firstname}{Lastname}{Full Stack Software Engineer}{\contactline{\href{https://www.mazumder.me}{mazumder.me}}{\href{https://www.github.com/sansquoi}{sansquoi}}{\href{https://www.linkedin.com/mazumders}{mazumders}}{\href{mailto:shubham.mazumder@gmail.com}{first.last@email.com}}{\href{tel:+1999999999}{9999999999}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.80\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{QodeAris Pvt. Ltd.}
\descript{| R\&D Intern}
\location{Sep 2025 – Mar 2026 | Pune, Maharashtra, India}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\item Architected a secure end-to-end IoT system connecting ESP32 devices to AWS IoT Core via a Node.js backend using MQTT over TLS, implementing Fleet Provisioning for automated device onboarding and certificate management.
\item Developed and deployed a solar-powered, cellular-connected autonomous weather station using ESP32 and LTE modem, integrating RS485 sensors and optimizing power usage with deep sleep cycles.
\item Secured backend infrastructure with AWS API Gateway and IAM (SigV4), while debugging critical issues including MQTT buffer limits, and AWS policy mismatches in production systems.
\end{tightemize}
\sectionsep


\runsubsection{Arusan Automation}
\descript{| R\&D Intern}
\location{Jun 2024 – Aug 2024 | Pune, Maharashtra, India (Remote/Hybrid)}
\vspace{\topsep}
\begin{tightemize}
\sectionsep
\item Designed and developed multiple hardware–software integrated projects including Smart Blind Stick, ESP32 Cloud Data Logger, Weight Measuring Device, Smart Glasses (prototype), and KalaChakra Smart Bell System.
\item Programmed ESP32-based IoT and automation systems in C++ (Arduino IDE), integrating sensors, actuators, cloud connectivity, and real-time communication.
\item Prototyped AI-based assistive applications in Python, implementing OCR, facial recognition (DeepFace), and voice command modules.
\end{tightemize}
\sectionsep


\runsubsection{Think of It Foundation}
\descript{| Web Scraping Intern }
\location{Jun 2023 – Oct 2023 | Pune, Maharashtra, India (Remote)}
\begin{tightemize}
\sectionsep
\item Extracted, organized, and analyzed electoral data from government websites, streamlining data collection.
\item Automated repetitive tasks to increase efficiency, reducing manual data entry by 40 times.
\item Developed scripts to enhance the speed of data extraction, enabling faster decision-making.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{WAREHOUSE AUTONOMY USING MARL}
\descript{| UNITY, PYTHON, DRQN, LSTM}
\location{Final Year Project | 2025 -- 2026}
\begin{tightemize}
\item Developing a MARL framework in Unity for autonomous warehouse robot navigation using DRQN and LSTM-based decision systems.
\item Optimizing reward shaping, agent coordination, and pathfinding in partially observable environments.
\item Simulating dynamic warehouse layouts with multiple cooperative agents to improve task allocation and collision avoidance efficiency.
\end{tightemize}
\sectionsep

\runsubsection{CANE VISION}
\descript{| IoT, MACHINE LEARNING}
\location{2023}
\begin{tightemize}
\item Developed a smart blind stick using ESP32, ESP32-CAM, and ultrasonic sensors; presented at I3CEET and filed for a design patent.
\item Implemented object detection and obstacle awareness features with haptic feedback to assist visually impaired users during navigation.
\item Integrated embedded hardware, sensor communication, and real-time alert systems for practical outdoor usability.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2020	     & Finalist & Lorem Ipsum\\
% 2018	     & $2^{nd}$ & Dolor Sit Amet\\
% 2015	     & Finalist  & Cras posuere\\
% \\
% \end{tabular}
% \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.25\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
\sectionsep
Python \textbullet{} JavaScript \textbullet{} Java \textbullet{} SQL 
\textbullet{} HTML \textbullet{} CSS \textbullet{} Embedded C \textbullet{} MicroPython

\sectionsep

\subsection{AI/ML \& Agentic AI}
\sectionsep
RAG \textbullet{} Agentic AI Systems 
\textbullet{} LLM Integration \textbullet{} Prompt Engineering \textbullet{} Model Evaluation \textbullet{} AI Workflows

\sectionsep

\subsection{Libraries/Frameworks}
\sectionsep
 TensorFlow \textbullet{} PyTorch 
\textbullet{} LangChain \textbullet{} Hugging Face Transformers \textbullet{} React

\sectionsep

\subsection{Tools/Platforms}
\sectionsep
Git \textbullet{} REST APIs \textbullet{} Vector Databases 
 \textbullet{} Microcontrollers \textbullet{} Sensors 
\textbullet{} CAD
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{DY Patil International University}
\descript{Bachelor's in Computer Science (AI Specialization)}
\location{Aug 2022 - Present | Pune, Maharashtra}
School of Computer Science Engg. \& Applications \\
\location{India}

\subsection{Army Public School, Kirkee}
\descript{Higher Education}
\location{April 2022 | Pune, Maharashtra}
Physics, Chemistry and Mathematics with Information Technology \\
\location{India}

\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     REFERENCES
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards and Recognition} 
\textbullet{}Memristor Nano-Finger Research: Presented at ACMESGA 2k24 Conference\\
\textbullet{}Cane Vision: Presented at the I3CEET\\
\textbullet{}DYPIU Excellence Award Scholarship \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}

% \subsection{Graduate}
% Graduate Algorithms \textbullet{}\\ 
% Advanced Computer Architecture \textbullet{}\\ 
% Operating Systems \textbullet{}\\ 
% Artificial Intelligence \textbullet{}\\
% Visualization For Scientific Data \\
% \sectionsep

% \subsection{Undergraduate}

% Database Management Systems \textbullet{}\\
% Object Oriented Analysis and Design \textbullet{}\\
% Artificial Intelligence and Expert Systems \textbullet{}\\
% Scripting Languages and Web Tech \textbullet{}\\
% Software Engineering \\

\end{minipage} 
\end{document}  \documentclass[]{article}

